---
title: "PMarquardt_HW4"
author: "Paul Marquardt"
date: "June 6, 2018"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Question 1
### Question 1a: Install the fivethirtyeight package
```{r}
install.packages(fivethirtyeight)
```

### Question 1b: In the listing of Data sets in package ‘fivethirtyeight,’ assign the 22nd data set to
an object ‘df.’
```{r}
library(fivethirtyeight)
df <- college_recent_grads
```
### Question 1c: Use a more detailed list of the data sets to write out the URL in a comment to the
related news story.
```{r}

```
### Question 1d: Using R command(s), give the dimensions and column names of this data frame
```{r}
dim(college_recent_grads)
colnames(college_recent_grads)
```
## Question 2
### Question 2a: Write an R command that gives you the column names of the data frame. Right after
that, write one that counts the number of columns but not rows. Hint: The number
should match one of your numbers in Question 1d for dimensions.
```{r}
library(plyr)
cn <- colnames(college_recent_grads)
df <- data.frame(cn)
count(df)
```

### Question 2b: . Generate a count of each unique major_category in the data frame. I recommend using
libraries to help. I have demonstrated one briefly in live-session. To be clear, this
should look like a matrix or data frame containing the major_category and the
frequency it occurs in the dataset. Assign it to major_count.
```{r}
mc <- data.frame(college_recent_grads)
# ddply(mc$major_category,summarise,unique_categories=length(unique(order_no)))
 library(dplyr)
mc %>%
   group_by(major_category) %>%
  summarise(n_distinct(major_category))
```
### Question 2c: To make things easier to read, enter par(las=2) before your plot to make the text
perpendicular to the axis. Make a barplot of major_count. Make sure to label the title
with something informative (check the vignette if you need), label the x and y axis, and
make it any color other than grey. Assign the major_category labels to their respective
bar. Flip the barplot horizontally so that bars extend to the right, not upward. All of
these options can be done in a single pass of barplot(). Note: It’s okay if it’s wider than
the preview pane.
```{r}
library(fivethirtyeight)
ds <- college_recent_grads
ds
# vignette("college_recent_grads", package = "fivethirtyeight")
mjc <- c(ds$rank, ds$major, ds$major_category, ds$total)
mjc
barplot(height = mjc,
  main = "Majors and thier respective ranks",
  xlab = "rank",
  ylab = "major",
  col = "red"
  )
```
### Question 2d: Write the fivethirtyeight data to a csv file. Make sure that it does not have row labels
```{r}
crg <- data.frame(college_recent_grads)
# crg
# getwd()
write.csv(crg, file = "HW3Question2d.csv",row.names = FALSE)
```
### Question 3a: Start a new repository on GitHub for your SMU MSDS homework. On your local
device, make sure there is a directory for Homework at the minimum; you are
welcome to add whatever you would like to this repo in addition to your requirements
here
```{r}
# git remote add origin https://github.com/ubergeekin/MSDS6306.git
# git pull origin master
dir.create("homework")
list.files()
```
### Question 3b: . Create a README.md file which explains the purpose of the repository, the topics
included, the sources for the material you post, and contact information in case of
questions. Remember, the one in the root directory should be general. You are
welcome to make short READMEs for each assignment individually in other folders.
```{r}

```

### Question 3c: In one (or more) of the nested directories, post your RMarkdown script, HTML file,
and data from ‘fivethirtyeight.’ Make sure that in your README or elsewhere that
you credit fivethirtyeight in some way
```{r}

```
### Question 3d: In your RMarkdown script, please provide the link to this GitHub so the grader can see
it.
```{r}

```
### Question 4: Please find the swirl output in the file upload section of assignments :)
```{r}

```